A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-11-20 index.Rmd
changed to rticles -- still no luck with sageapa

---
output:
  pdf_document:
    keep_tex: true
    template: sagej_template.tex
bibliography: ["references.bib"]
biblio-style: apa
link-citations: yes
citation_package: biblatex
---

\runninghead{Smith and Wittkopf}

\title{workingtitle}

\author{Clemens Schmid\affilnum{1}}

\affiliation{\affilnum{1}Institute of Pre- and Protohistoric Archaeology, Kiel University, Kiel, DE}

\corrauth{
Clemens Schmid,
Institut für Ur- und Frühgeschichte,
Christian-Albrechts-Universität,
D - 24098 Kiel.
}

\email{clemens@nevrome.de}

\begin{abstract}
This paper is nice.
\end{abstract}

\keywords{Bronze Age, Burial Traditions, Cultural Evolution, Cultural Transmission}

\maketitle

>>>>

---
title: A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe
runninghead: Schmid.
author:
- name: Clemens Schmid
  num: 1
address:
- num: 1
  org: Institute of Pre- and Protohistoric Archaeology, Kiel University, Kiel, Germany
corrauth: "Clemens Schmid, Institut für Ur- und Frühgeschichte, Christian-Albrechts-Universität, D - 24098 Kiel."
email: clemens@nevrome.de
abstract: "Petersilie."
keywords: Bronze Age, Burial Traditions, Cultural Evolution, Cultural Transmission
classoption:
  - Afour
  - times
bibliography: references
bibliographystyle: apalike
output:
  rticles::sage_article:
    keep_tex: yes
---

```{r child = '01_Introduction.Rmd'}
```

```{r child = '02_Materials_and_Methods.Rmd'}
```

```{r child = '03_Results.Rmd'}
```

```{r child = '04_Discussion.Rmd'}
```
